---
title: "RWorksheet_Condag#1"
author: "Angel Blase Condag"
date: "2024-09-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. AGE VECTOR
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 
         50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```
a. DATA POINTS
```{r}
   length(age)
```
 
  
2. RECIPROCAL
```{r}
  reciprocal <- 1 / age
  library("MASS")
  fractions(reciprocal)
```


3. NEW AGE
```{r}
  new_age <- c(age, 0, age)
  print(new_age)
```
What happen to the new_age?

    The new_age vector contains all the original values in the age vector, followed by a zero,
    and then the original values of age vector again.


4. SORT
```{r}
  sort(age)
```
 
  
5. MINIMUM AND MAXIMUM VALUE
```{r}
  min(age)
  max(age)
```
 
 
6. DATA VECTOR
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
```
a. DATA POINTS
```{r}
  length(data)
```
  
  
7. DOUBLE
```{r}
  double <- 2 * data
  print(double)
```
What happen to the data?

  The value of the elements in the data vector doubled or should I say multiplied by 2.


8. SEQUENCE, MEAN, SUM
8.1 Integers from 1 to 100
```{r}
integers <- seq(1:100)
print(integers)
```
8.2 Numbers from 20 to 60
```{r}
numbers <- seq(20,60)
print(numbers)
```
8.3 Mean of numbers from 20 to 60
```{r}
mean <- mean(20:60)
print(mean)
```
8.4 Sum of numbers from 51 to 91
```{r}
sum <- sum(51:91)
print(sum)
```
8.5 Integers from 1 to 1,000
Code and Output from 8.1 to 8.4
```{r}
thousands <- seq(1:1000)
thousands
```
a. Data Points from 8.1 to 8.4?
```{r}
length(integers) + length(numbers) + length(mean) + length(sum)
```

c. Maximum Data Points until 10
```{r}
max(thousands[thousands <- 10])
```


9. Filter
```{r}
Filter(function(i) { all(i %% c(3, 5, 7) != 0)}, seq(100))
```


10. Backwards of the integers from 1 to 100.
```{r}
backwards <- seq(100, 1)
print(backwards)
```


11. Natural numbers below 25 that are multiples of 3 or 5.
```{r}
numbers <- 1:24
multiples <- numbers[numbers %% 3 == 0 | numbers %% 5 == 0]
print(multiples)
sum_multiples <- sum(multiples)
print(sum_multiples)
```
a. Data Points from 10 to 11:
    11


12. BLOCK
```{r}
#x <- {0 + x + 5 +}
```
Describe the output: 
  The r code turns out to be an error because the expression inside the curly braces is incomplete because it ends with a "+".


13. SCORE VECTOR
```{r}
score <- c(71, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
score[2]
score[3]
```


14. A VECTOR
```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
print(a,na.print="-999")
```
Describe the output:
  Each element in the vector is printed, and the NA values appear as "-999" in the output.
  
  
15. SPECIAL FUNCTION
```{r}
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
```

