---
title: "RWorksheet_Condag#1"
author: "Angel Blase Condag"
date: "2024-09-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. AGE VECTOR
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 
         50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```
a. Data Points
```{r}
   length(age)
```
b. Code and Output

# Code:
  length(age)
  
# Output:
  34
  
  
2. Reciprocal
```{r}
  reciprocal <- 1 / age
  library("MASS")
  fractions(reciprocal)
```
# Code:
  reciprocal <- 1 / age
  library("MASS")
  fractions(reciprocal)
  
# Output:
    1/34 1/28 1/22 1/36 1/27 1/18 1/52 1/39 1/42 1/29 1/35 1/31 1/27
    1/22 1/37 1/34 1/19 1/20 1/57 1/49 1/50 1/37 1/46 1/25 1/17 1/37
    1/42 1/53 1/41 1/51 1/35 1/24 1/33 1/41
    
    
3. New Age
```{r}
  new_age <- c(age, 0, age)
  print(new_age)
```
What happen to the new_age?

    It prints all the numbers in the age vector, added zero after the last number,
    and prints all the numbers in the age vector again.


4. Sort
```{r}
  sort(age)
```
# Code:
  sort(age)
  
# Output:
  17 18 19 20 22 22 24 25 27 27 28 29 31 33 34 34 35 35 36 37
  37 37 39 41 41 42 42 46 49 50 51 52 53 57
  
  
5. Minimum and Maximum value
```{r}
  min(age)
  max(age)
```
# Code:
  min(age)
  max(age)
  
# Output:
  min = 17
  max = 57
 
  
6. DATA VECTOR
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
```
a. Data Points
```{r}
  length(data)
```
b. Code and Output

# Code:
  length(data)
  
# Output:
  12
  
2. Double
```{r}
  double <- 2 * data
  print(double)
```
What happen to the data?

  The value of the decimals in the data vector doubled.

8. Sequence


